### 2019-02-27 sections/abstract.tex
soften abstract a bit

% Inquiry
TOP has been around for more than a decade, in the form of iTasks, which is tailored for real-world usability.
So far, it has not been given a formalization which is very suitable for formal reasoning.

@@

% Importance
TOP has been employed in projects with the Dutch coast guard, tax office, and navy.
Our work matters because Formal program verification is important for mission-critical software, especially for systems with concurrency.

>>>>

% Inquiry
TOP has been around for more than a decade, in the form of iTasks, which is tailored for real-world usability.
So far, it has not been given a formalisation which is suitable for formal reasoning.

@@

% Importance
TOP has been employed in projects with the Dutch coast guard, tax office, and navy.
Our work matters because formal program verification is important for mission-critical software, especially for systems with concurrency.
